### 2019-01-05 Sections/protocols_for_the_quantum_internet.tex
+Delay line memory

At the physical level, there are two main approaches we could use to put optical states into memory. The first is simply to employ delay lines, either in free-space or in fibre. The second is to interface the state with a non-optical system with a long lifetime, which holds the information content until needed and out-coupled. This can be achieved using, for example, the light-matter interfacing techniques discussed in Sec.~\ref{sec:opt_inter}.

>>>>

At the physical level, there are two main approaches we could use to put optical states into memory. The first is simply to employ optical delay lines\index{Optical delay lines} (shown in Fig.~\ref{fig:delay_line_mem}), either in free-space or in fibre. The second is to interface the state with a non-optical system with a long coherence lifetime, which holds the information content until needed before being out-coupled. This can be achieved using, for example, the light-matter interfacing techniques discussed in Sec.~\ref{sec:opt_inter}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{delay_line_memory}
\captionspacefig \caption{Simple architecture for a controllable optical quantum memory using an optical delay line. A length of optical fibre (or free-space), with roundtrip time $\tau_\mathrm{delay}$, couples to a fast controllable switch, with switching time \mbox{$\tau_\mathrm{switch}\ll\tau_\mathrm{delay}$}. The switch allows the optical state to be coupled into the loop, maintained there for an arbitrary number of roundtrips, and then coupled out. The storage time of the memory is restricted to being integer multiples of the roundtrip time, \mbox{$\tau_\mathrm{storage}=n\cdot\tau_\mathrm{delay}$}, where \mbox{$n\in\mathbb{Z}_+$} is the number of roundtrips. If the efficiency of the fibre-loop is $\eta$, the effective efficiency of the quantum memory after readout is \mbox{$\eta_\mathrm{eff}=\eta^n$}.}\label{fig:delay_line_mem}	
\end{figure}
